### 2018-07-20 sections/signal_background_modeling.tex
Additional fixes

\subsubsection{Fake taus}
\label{sec:faketaus}
In the $\Htautau$ search, the background with one or more fake $\tauhad$ candidates is mainly arising from $\ttbar$ or
multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. The simulation study shows that b-jet faking rate is quite low and the fake $\tauhad$ candidates primarily result from the misidentification of light-quark jets. This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is dropped.

>>>>

\subsubsection{Fake taus}
\label{sec:faketaus}
In the $\Htautau$ search, the background with one or more fake $\tauhad$ candidates is mainly arising from $\ttbar$ or
multijet production, depending on the analysis channel, with $W$+jets production contributing to a lesser extent. 
Studies based on the simulation show that , for all above processes, fake $\tauhad$ candidates primarily result from the 
misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
It is also found that the fake rate decreases as the $\tauhad$ candidate $\pt$ increases for all jet flavours.

This background is estimated directly from data by defining control regions (CR) enriched in fake $\tauhad$ candidates via loosened $\tauhad$ requirements. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the leading (trailing) $\tauhad$ candidate 
in the $\lephad$ ($\hadhad$) channel is required to be of loose-not-medium quality, and the requirement on its charge is dropped.

### 2018-07-20 sections/systematic_uncertainties.tex
Additional fixes

\textbf{Update discussion on small bkgs systs for tautau (recently updated).}

@@

Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
(we assume already two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.

@@

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

>>>>

@@

Uncertainties on the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
(it is assumed that two jets come from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
i.e. 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively.
Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.

@@

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted samples. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the shape difference between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. Finally, the normalisation of the fake $\tauhad$ background in each SR is determined by the data during the fit procedure, and thus so is its uncertainty. In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.
